Circuits

### 2017-04-10 paper.tex
Things have been updated
Last Changes

\newcommand{\bd}[1]{\mathbf{#1}} % for bolding symbols
\newcommand{\RR}{\mathbb{R}} % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}} % for Integers
\newcommand{\MB}{\mathbb{B}_{\matsym}} % for Integers
\newcommand{\SB}{\mathbb{B}_{\sym}} % for Integers
\newcommand{\col}[1]{\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
\newcommand{\stab}{\text{\textbf{Stab}}}
\newcommand{\setstab}{\text{\textbf{SetStab}}}
\newcommand{\matstab}{\text{\textbf{MatStab}}}
\newcommand{\inv}{\text{\textbf{inv}}}
\newcommand{\aut}{\text{\textbf{Aut}}}
\newcommand{\kernal}{\text{\textbf{ker}}}
\newcommand{\alt}{\text{\textbf{Alt}}}
\newcommand{\sym}{\text{\textbf{Sym}}}
\newcommand{\rank}{\text{\textbf{rk}}}
\newcommand{\orb}{\text{\textbf{Orb}}}
\newcommand{\SP}{\text{\textbf{SP}}}
\newcommand{\maj}{\text{\textbf{Maj}}}
\newcommand{\dom}{\text{\textbf{Dom}}}
\newcommand{\child}{\text{child}}
\newcommand{\countgate}{\text{count}}
\newcommand{\agree}{\text{AGREE}}
\newcommand{\supp}{\text{SUPP}}
\newcommand{\rankparam}{\text{PARAM}}

@@

\section{}

@@

\begin{lem}
  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\alpha \in
  U^{\underbar{\sp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
  with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim \gamma^{-1}_2$. Let $A
  \times B = \dom (L(g))$.

@@

\begin{lem}
  Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
  U^{\underbar{\sp(g)}}$ and $\gamma: U \rightrrow [n]$ such that
  $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
  $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
  \begin{align*}
    L^{EV}_\alpha (a,b):=
    \begin{cases*}
      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
    \end{cases*},
  \end{align*}
  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
  $\rk^u_p(L^0_\gamma)$
\end{lem}
\begin{proof}

\begin{lem}
  Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
  \in U^{\underbar{\sp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
  $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
  $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
  associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
  \begin{align*}
    L^{EV}_\alpha (a,b):=
    \begin{cases*}
      1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
    \end{cases*},
  \end{align*}
  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
  \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
\end{lem}
\begin{proof}
  First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
  iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
  from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
  all such $\gamma$.

  We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.

  Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
  $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
  exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
  $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
  transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
  $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
  1$.

  Now suppose that $L^0_\gamma (a,b) = 1$
\end{proof}

@@

Using the Immerman-Vardi Theorem, we can define an FP($\leq$) formula
$\rankpara$ such that $\langle [n], \leq\rangle \models \rankpara[g,p,u]$ iff
$\langle [n], \leq\rangle \models \phi_G[g] \land \phi_{\rank}[g]$ and the rank
gate $g$ (as per the interpretation) computes the rank over characteristic $p$
and has threshold $u$.

@@

@@

  We then have that
  \begin{align*}
    \vert S_n : \inv_{CFI(G)}(g) \vert \leq \vert S_n : \alt ([n] \setminus (X_1 \cup X_2)) \leq  \frac{n!}{(n-2k)!/2} \leq n^{2k+1},
  \end{align*}
  with the last inequality following for large enough $n$. We thus
  have from Theorem \ref{} that there is a symmetric circuit $D_n$
  that decides the CFI problem for $G_n$, and hence a family $(D_n)$
  that decides the CFI problem for the family of graphs $(G_n)$. From
  the theorem of Dawar et al. \cite{}, it follows that there is as
  formula of FPC that decides the CFI query for $(G_n)$ contradicting
  our assumption.
\end{proof}
\end{document}

>>>>

\newcommand{\bd}[1]{\mathbf{#1}} % for bolding symbols
\newcommand{\RR}{\mathbb{R}} % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}} % for Integers
\newcommand{\MB}{\mathbb{B}_{\matsym}} % for Integers
\newcommand{\SB}{\mathbb{B}_{\sym}} % for Integers
\newcommand{\col}[1]{\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
\newcommand{\stab}{\text{\textbf{Stab}}}
\newcommand{\setstab}{\text{\textbf{SetStab}}}
\newcommand{\matstab}{\text{\textbf{MatStab}}}
\newcommand{\inv}{\text{\textbf{inv}}}
\newcommand{\aut}{\text{\textbf{Aut}}}
\newcommand{\kernal}{\text{\textbf{ker}}}
\newcommand{\alt}{\text{\textbf{Alt}}}
\newcommand{\sym}{\text{\textbf{Sym}}}
\newcommand{\rank}{\text{\textbf{rk}}}
\newcommand{\orb}{\text{\textbf{Orb}}}
\newcommand{\SP}{\text{\textbf{SP}}}
\newcommand{\maj}{\text{\textbf{Maj}}}
\newcommand{\dom}{\text{\textbf{Dom}}}
\newcommand{\child}{\text{child}}
\newcommand{\countgate}{\text{count}}
\newcommand{\agree}{\text{AGREE}}
\newcommand{\supp}{\text{SUPP}}
\newcommand{\rankparam}{\text{PARAM}}
\newcommand{\consp}{\text{sp}}
\newcommand{\row}{\text{row}}
\newcommand{\column}{\text{col}}
\newcommand{\rowsp}{\text{r}}
\newcommand{\colsp}{\text{c}}
\newcommand{\EV}{\text{EV}}
\newcommand{\spstab}[1]{\stab (\consp (#1))}

@@

@@

\begin{lem}
  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$. Let $\alpha \in
  U^{\underbar{\consp(g)}}$, and suppose $\gamma_1, \gamma_2: U \rightarrow [n]$
  with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim \gamma^{-1}_2$. Let $A
  \times B = \dom (L(g))$.

@@

% \begin{lem}
%   Let $g$ be a matrix symmetric gate in $C_n$ with children $H$. Let $\alpha \in
%   U^{\underbar{\consp(g)}}$ and $\gamma: U \rightarrow [n]$ such that
%   $gamma^{-1}\sim \alpha$. Let $A \times B = \dom (L(g))$ and define
%   $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
  % \begin{align*}
  %   L^{EV}_\alpha (a,b):=
    % \begin{cases*}
    %   1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
   % \end{cases*},
%  \end{align*}
%  where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
%  \sim \beta\}$. Then $L^0_\gamma = L^{EV}_\alpha$ and $\alpha \in \EV(g)$ iff
%  $\rk^u_p(L^0_\gamma)$
%\end{lem}
%\begin{proof}
%  
%\end{proof}

% \begin{lem}
%   Let $g$ be a matrix-symmetric gate in $C_n$ with children $W_g$. $Let \alpha
%   \in U^{\underbar{\consp(g)}}$ and let $\gamma: U \rightarrow [n]$ such that
%   $\gamma^{-1} \sim \alpha$. Let $A \times B = \dom (L(g))$, and let
%   $f:\{0,1\}^{A \times B} \rightarrow \{0,1\}$ be the matrix-symmetric function
%   associated with $g$. Define $L^{EV}_\alpha: A \times B \rightarrow \{0,1\}$ by
  % \begin{align*}
  %   L^{EV}_\alpha (a,b):=
%     \begin{cases*}
%       1 & if $A_h \cap \EV_h \neq \emptyset$ 0 & otherwise
%     \end{cases*},
%   \end{align*}
%   where for $h \in W_g, A_h:= \{\beta \in U^{\underline{\sp(h)}} \vert \alpha
%   \sim \beta\}$. Then $\alpha \in \EV_g$ iff $f(L^\EV_\alpha)$.
% \end{lem}
% \begin{proof}
%   First note that if $\alpha \in U^{\underbar{\sp{g}}}$ then $\alpha \in \EV_g$
%   iff we have that $C_n[\gamma \mathcal{A}](g)= f (L^0_\gamma) = 1$. Notice that
%   from Lemma \ref{} that this holds for any particular $\gamma$ iff it holds for
%   all such $\gamma$.

%   We now show that $L^\EV_\alpha = L^0_\gamma$, and so complete the proof.

%   Suppose for $(a,b) \in A \times B$ we have that $L^\EV_\alpha(a,b) = 1$. Let
%   $h:= L(g)(a,b)$. It follows that $A_h \cap \EV_h \neq \emptyset$, i.e there
%   exits $\beta \in \sp(h)$ such that $\beta \sim \alpha$ and there exists
%   $\gamma_h \in \Gamma(h)$ such that $\gamma^{-1}_h \sim \beta$. It follows from
%   transitivity and Lemma \ref{} that $\gamma_h \sim \alpha$ and so
%   $L^0_\alpha(a,b) = C_n[\gamma \mathcal{A}](h) = C_n[\gamma_h \mathcal{A}](h) =
%   1$.

%   Now suppose that $L^0_\gamma (a,b) = 1$
% \end{proof}

@@

Using the Immerman-Vardi Theorem, we can define an FP($\leq$) formula
$\rankparam$ such that $\langle [n], \leq\rangle \models \rankparam,a[g,p,u]$ iff
$\langle [n], \leq\rangle \models \phi_G[g] \land \phi_{\rank}[g]$ and the rank
gate $g$ (as per the interpretation) computes the rank over characteristic $p$
and has threshold $u$.

@@

\pagebreak

\section{Computing the Rank of a Labelling in FPR}

In this section I discuss how to determine the rank a matrix labelling at some
gate $g$. This is a rough copy written for the purpose of discussion. In this
section we fix some circuit $C_n$ and some rank gate $g$ in $C_n$, with matrix
labelling $\omega$.

\begin{definition}
  Let $h \in H$, then $S \subseteq [n]$ is a row support iff $\forall \sigma \in
  \stab (\consp(g))$ whenever $\forall i \in S, \sigma i = i$ then $\row (\sigma
  h) = \row (h)$.
  \\~\\
  Similarly we can define the notion of a column support.
  \\~\\
  Let $r_h$ be the canonical row support and $c_h$ be the canonical column
  support.
\end{definition}

\begin{remark}
  Let $\sigma \in \spstab{g}$, then we know that $\sigma$ induces an action on
  the rows and columns such that the result is a row column permutation. We may
  associate with $\sigma$ a pair $(\sigma_r, \sigma_c) \in \sym_A \times
  \sym_B$, where $\sigma_r (i) = \row (\sigma h)$, for some $h \in H$, $\row (h
  = i)$ and similarly $\sigma_c (j) = \column (\sigma h)$, for some $h \in H$,
  $\column (h) = j$. The definition of a permutation on a circuit, and the
  stability group for $g$ gives us that such permutations must exist.
\end{remark}

The following lemma asserts a few basic facts about the (canonical) row and
column supports.

\begin{lem}
  Let $h \in H$, then $r_h \subset \consp(h)$, $c_h \subset \consp(h)$ and $c_r
  \cup r_h = \consp(h)$.
\end{lem}

We introduce here some useful notation.

\begin{definition}
  Let $S^r_h = \{ \sigma \in \stab (\consp(g)) : \sigma \vec{r_h} = \vec{r_h}
  \}$ and $G^r_h = \{ \sigma \in \stab(\consp(g)) : \row(\sigma h) = \row(h)\}$.
  Let $S^c_h = \{ \sigma \in \stab (\consp(g)) : \sigma \vec{c_h} = \vec{c_h}
  \}$ and $G^c_h = \{ \sigma \in \stab(\consp(g)) : \column(\sigma h) =
  \column(h)\}$.
\end{definition}

Clearly, by definition of a row and column support, $S^r_h \subseteq G^r_h$ and
$S^c_h \subseteq G^c_h$.
\\~\\
In this section some simplifying assumptions are made.

\begin{remark}
  In this section I assume for the moment that:
  \begin{itemize}
  \item $\consp (g) = \{\}$,
  \item $S^r_h = G^r_h$ and $S^c_h = G^c_h$, and
  \item $\forall h,h' \in H$ we have $\vert r_h \vert = \vert r_{h'} \vert$ and
    $\vert c_h \vert = \vert c_{h'} \vert$.
  \end{itemize}
\end{remark}

Let $k_r = \vert r_h \vert$ and $k_c = \vert c_h \vert$. In the following we let
$\vec{x} \in U^{k_r}$ and $\vec{y} \in U^{k_c}$. These vectors are thought of as
generic assignments to the row and column supports of some element $h \in H$. Of
course, the structure of the row and column supports of a particular $h \in H$
does matter, and two assignments may be valid or invalid depending on that
stricture. We now consider ways of `choosing' a particular element of $H$ that
has the `correct' structure for such a pair.
\\~\\
Then let for $h \in H$, let $\vec{x}_h: r_h \rightarrow U$ be defined by
$\vec{x}_h(i) = \vec{x}(\vec{r_h}^{-1}(i))$. Similarly, let $\vec{y}_h: c_h
\rightarrow U$ be defined by $\vec{y}_h(i) = \vec{y}(\vec{c_h}^{-1}(i))$. We can
think of the functions $(h, \vec{x}) \mapsto \vec{x}_h$ and $(h, \vec{y})
\mapsto \vec{y}_h$ as taking these respective tuples and assigning them to the
row and column supports of $h$.

\begin{lem}
  For each pair $(\vec{x}, \vec{y})$ there is an $h \in H$ such that $\vec{x}_h
  \sim \vec{y}_h$.
\end{lem}

Let us then define a function $\mu : U^{k_r} \times U^{k_c} \rightarrow H$,
where $\mu(\vec{x}, \vec{y})$ is the minimal $h \in H$ (in the order of the
structure) such that $\vec{x}_h \sim \vec{y}_h$. The above lemma tells us that
this function is indeed well-defined (in particular, it's total).

We note that if $\vec{x}_h \sim \vec{y}_h$ it follows that we can define
$(\vec{x}, \vec{y})$ an assignment to the support of $h$.

We then define the matrix $M(\vec{x}, \vec{y}) := (\vec{x}, \vec{y}) \in
\EV_{\mu(\vec{x}, \vec{y})}$.

We now define what it means for two matrices to be row-column equivalent.

\begin{definition}
  Let $M_1$ and $M_2$ be matrices over some field, with row and column indexes
  given by $(A_1, B_1)$ and $(A_2, B_2)$, respectively. We say that $M_1$ and
  $M_2$ are row-column equivalent iff there exists bijections $\alpha: A_1
  \rightarrow A_2$ and $\beta: B_1 \rightarrow B_2$ such that for all $(a,b) \in
  A_1 \times B_1$ we have that $M_1(a,b) = M_2 (\alpha (a), \beta (b))$. If
  $M_1$ and $M_2$ are row-column equivalent we say that $M_1 \sim M_2$.
\end{definition}

Suppose $\alpha_g \in U^{\sp(g)}$ an injection and fix a bijection $\gamma: U
\rightarrow [n]$ such that $\alpha_g \sim \gamma^{-1}$. We can then define
$L^\gamma: A \times B \rightarrow \{0,1\}$ by $L^\gamma(a,b) = C[\gamma
\mathcal{A}](\omega (a,b))$.
\\~\\
We note that, in fact, it is the choice of the assignment to the support of $g$,
i.e. $\alpha_g$, that really matters in the sense that for any two global
assignments that agree on the support of $g$ will produce row-column equivalent
matrices. The following lemma formalises this observation.

\begin{lem}
  Let $g$ be a matrix-symmetric gate in $C_n$ with children $H$ and matrix
  labelling $L(g)$. Let $\alpha_g \in U^{\consp(g)}$, and suppose $\gamma_1,
  \gamma_2: U \rightarrow [n]$ with $\gamma^{-1}_1 \sim \alpha$ and $\alpha \sim
  \gamma^{-1}_2$. Let $A \times B = \dom (L(g))$.

  For an input structure $\mathcal{A}$, let $L^\gamma: A \times B \rightarrow
  \{0,1\}$, where $L^{\gamma_2} (a,b):= C[\gamma \mathcal{A}] (L(g)(a,b))$.

  Then $L^{\gamma_1} \sim L^{\gamma_2}$.
\end{lem}
\begin{proof}
  We have that there exists a unique $\pi \in \sym_n$ such that $\pi \gamma_1 =
  \gamma_2$. Moreover, since $\gamma^{-1}_1$ and $\gamma^{-1}_2$ are both
  consistent with $\alpha$, it follows that $\pi$ must fix $\sp(g)$. Thus $L(g)
  \sim \pi L(g)$, and so there exists $(\sigma, \lambda)$ such that $\pi L(g) =
  L(g) \cdot (\sigma, \lambda)$.

  We then have that,
  \begin{align*}
    L^{\gamma_1} (a,b) &= C_n[\gamma_1 \mathcal{A}](L(g)(a,b))\\
                       & = C_n[\pi \gamma_1 \mathcal{A}][\pi L(g)(a,b)] \\
                       & = C_n[\gamma_2 \mathcal{A}][L(g)((\sigma, \lambda)(a,b))]\\
                       & = L^{\gamma_2} ((\sigma, \lambda) (a,b)),
  \end{align*}
  and it follows that $L^{\gamma_1} \sim L^{\gamma_2}$.
\end{proof}

\begin{lem}
  Let $h_1, h_2 \in H$ and $\sigma_1, \sigma_2 \in \spstab{g}$. Suppose
  $\sigma_1 \vec{r_{h_1}} = \sigma_2 \vec{r_{h_2}}$. Then $\row (\sigma_1 h_1) =
  \row (\sigma_2 h_2)$.
\end{lem}
\begin{proof}
  There exists $\sigma \in \spstab{g}$ such that $\sigma \vec{r_{h_1}} =
  \vec{r_{h_2}}$, and so $\sigma_1 \vec{r_{h_1}} = \sigma_2 \sigma
  \vec{r_{h_1}}$, and thus $(\sigma_2 \sigma)^{-1} \sigma_1 \vec{r_{h_1}} =
  \vec{r_{h_1}}$. It follows that $(\sigma_2 \sigma)^{-1} \sigma_1 \in S^r_{h_1}
  \subseteq G^r_{h_1}$, and so $\row ((\sigma_2 \sigma)^{-1} \sigma_1 h_1) =
  \row (h_1)$. Thus $((\sigma_2)_r \sigma_r)^{-1} (\sigma_1)_r \row (h_1) = \row
  (h_1)$.

  It follows that $\row (\sigma_1 h ) = (\sigma_1)_r \row (h_1) = (\sigma_2)_r
  \sigma_r\row (h_1) = (\sigma_2)_r \row (\sigma h_1) = (\sigma_2)_r \row (h_2)
  = \row (\sigma_2 h_2)$.

  % Uses assumption (-check-)

\begin{claim}
  For $h \in H$ and $\sigma \in \stab(\consp (g))$, we have that
  $\vec{r}_{\sigma h_1} = \sigma \vec{r}_{h_1}$.
\end{claim}
\begin{proof}
  Proof needed, proof strategy in book
\end{proof}

\begin{lem}
  Let $h_1, h_2 \in H$ and $\sigma_1, \sigma_2 \in \stab (\consp(g))$ such that
  $\sigma_1 \vec{r}_{h_1} = \sigma_2 \vec{r}_{h_2}$ and there exists $\sigma \in
  \stab(\consp (g))$ such that $\row (\sigma h_1) = \row (\sigma h_2)$, then
  $\row (\sigma_1 h_1) = \row (\sigma_2 h_2)$.
\end{lem}
\begin{proof}
  proof in book
  % So $\row (\sigma h_1) = \row (h_2)$, and so $\sigma \vec{r} = \vec{r}_{\sigma h_1} =
  % \vec{r}_{h_2}$.
\end{proof}

Let $\Pi^\gamma_{(\vec{x}), \vec{y}}(\mu(\vec{x}, \vec{y}))$ be the action on
$\mu (\vec{x}, \vec{y})$ defined the action on the support given by
$\Pi^\gamma_{(\vec{x}, \vec{y})}(\vec{\sp(h)}) = \gamma ((\vec{x}, \vec{y})$.

\begin{claim}
  Let $\vec{y}, \vec{y}' \in U^{k_r}$ and $\vec{x}, \vec{x} \in U^{k_c }$ then
  \begin{align*}
    \row (\Pi^\gamma_{(\vec{x}, \vec{y})}(\mu(\vec{x}, \vec{y}))) = \row (\Pi^\gamma_{(\vec{x}, \vec{y}')}(\mu(\vec{x}, \vec{y}'),
  \end{align*}
  and
  \begin{align*}
    \column(\Pi^\gamma_{(\vec{x}, \vec{y})}(\mu(\vec{x}, \vec{y}))) = \column
    (\Pi^\gamma_{(\vec{x}', \vec{y})}(\mu(\vec{x}', \vec{y}).
  \end{align*}
\end{claim}
\begin{proof}
  proof in book
\end{proof}

We let $\alpha: U^{k_r} \rightarrow A$, $\beta: U^{k_c} \rightarrow B$ be
defined by $\alpha (\vec{x}) = \row (\Pi^\gamma_{(\vec{x}, \vec{y})} (\mu
(\vec{x}, \vec{y})$ for some $\vec{y} \in U^{k_c}$. Similarly we can define
$\beta (\vec{y})$.

The above claim tells us that this definition is well defined.

\begin{claim} 
  Both $\alpha$ and $\beta$ are bijections.
\end{claim}
\begin{proof}
 proof in book 
\end{proof}

\begin{thm}
  $L$ is row-column equivalent to $M$.
\end{thm}
\begin{proof}[proof of above theorem]
  \begin{align*}
    M(\vec{x}, \vec{y}) &\iff (\vec{x}, \vec{y}) \in \EV_{\mu({\vec{x}, \vec{y}})} \\  
                        &\iff C_n [\gamma \mathcal{A}] (\Pi^\gamma_{(\vec{x}, \vec{y})} (\mu (\vec{x}, \vec{y}))) \\
                        &\iff C_n [\gamma \mathcal{A}] (\omega (\alpha (\vec{x}), \beta (\vec{y}))) \\
                        &\iff L^\gamma (\alpha (\vec{x}), \beta (\vec{y}))
  \end{align*}
  The above calculation, combined with the fact that $\alpha$ and $\beta$ are
  bijections, proves the result.
\end{proof}

@@

  We then have that
  \begin{align*}
    \vert S_n : \inv_{CFI(G)}(g) \vert \leq \vert S_n : \alt ([n] \setminus (X_1 \cup X_2)) \leq  \frac{n!}{(n-2k)!/2} \leq n^{2k+1},
  \end{align*}
  with the last inequality following for large enough $n$. We thus
  have from Theorem \ref{} that there is a symmetric circuit $D_n$
  that decides the CFI problem for $G_n$, and hence a family $(D_n)$
  that decides the CFI problem for the family of graphs $(G_n)$. From
  the theorem of Dawar et al. \cite{}, it follows that there is as
  formula of FPC that decides the CFI query for $(G_n)$ contradicting
  our assumption.
\end{proof}

\end{document}
